Evaluating Deep Learning Methods for Word Segmentation of Scripta Continua Texts in Old French and Latin

### 2020-03-30 article/article.tex
Small update on some proof-reading post-peer-review

\documentclass{jdmdh}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{tabularx}
\newcolumntype{C}{>{\arraybackslash}X} % centered "X" column

@@

Tokenization of space-less strings is a task that is specifically difficult for computers as compared to "whathumanscando". \textit{Scripta continua} is a writing phenomenon in which words are separated by spaces that disappeared around the 8th century (see \citet{zanna1998lecture}). Nevertheless, spacing can be somewhat erratic in later centuries writings as \citet{stutzmann} explains (\textit{cf.} Figure \ref{fig:4lines}) and it becomes an issue for OCR, as continuous bag of word is only interesting when those are not glued together. In the context of text mining of HTR or OCR output, lemmatization and tokenization of medieval western languages can be a pre-processing step for further research to sustain analyses such as authorship attribution or simply allow full-text search.

@@

It must be stressed in this study that the difficulty inherent to segmentation is different for \textit{scripta continua} than the one for languages such as Chinese for which an already impressive amount of work has been done. Chinese word segmentation has lately been driven by deep learning methods: \citet{chen2015long} defines a process based on LSTM model, while \citet{yu2019learning} uses bi-directional GRU and CRF. \footnote{\citet{huang2019realistic} actually gave us the denomination used here: word boundary (WB) and word content (WC).}

@@

For evaluation purposes, and to reduce the number of input classes, two options for data transcoding were used: a lower-case normalization and a "reduction to the ASCII character set" feature (fr. \ref{fig:normalization}). On this point, a lot of issues were encountered with transliteration of medieval paelographic characters that were part of the original datasets, as they are poorly interpreted by the \texttt{unidecode} python package. Indeed, \texttt{unidecode} will simply remove characters it does not understand. A derivative package named \texttt{mufidecode} was built for this reason(\citet{thibault_clerice_2019_3237731}): it takes precedent over \texttt{unidecode} equivalency tables when the data is known of the Medieval Unicode Font Initiative (MUFI, \citet{mufi}).

@@

Aside from normalizations of the input and output, three different model structures were tested. Every model is composed of one encoder, as described below, and one Linear Classifier which classifies into 5 classes : Start of Sentence (= SOS), End of Sentence (= EOS), Padding (= PAD), Masked Token (= Word Content), Space (= Word Boundary) \footnote{For final scores, SOS, EOS and PAD were ignored.}.

The encoders are the following (configurations in parenthesis):

@@

\subsubsection{Datasets}

@@

\begin{itemize}
    \item 193,734 training examples (group of words);
    \item 23,581 validation examples;
    \item 25,512 test examples
    \item Number of classes in testing examples: 482,776 WC; 169,094 WB
    \item Number of classes in unknown examples: 26,393 WC; 10,193 WB
\end{itemize}

Examples were generated automatically. They are between 2 and 8 words-length. In order to recreate the condition of OCR noise, dots were added randomly (0.2) between words. In order to augment the dataset, words are randomly (0.1) passed over the next example\footnote{This data augmentation was limited to one word per sample}. If a minimum size of 7 characters was not met in the input sample, another word would be added to the chain, independently of the maximum number of words. The example however should not go beyond 100 characters. The results corpora should be varied in sizes as shown by Figure \ref{fig:word_sizes}. The corpora contains 193 different characters when not normalized, in which some MUFI characters appears few hundred times (\textit{cf.} Table \ref{tab:mufi_examples}).

@@

\subsubsection{Results}

@@

\subsubsection{Unknown texts}

While all models using CNN show improvement over the baseline, the models definitely do not significantly outperform (\textless 0.02 FScore). There is a reason for this: the baseline already performs nearly perfectly on the test corpus. The dictionary attack using n-grams did actually perform well. Therefore, an additional evaluation method was constructed. The baseline and the best achieving deep-learning model (CNN P) were evaluated on a secondary test corpus composed of texts of a different domain. This new corpus is composed by 4 texts and counts 742 examples : the diplomatic edition of the \textit{Graal} (\citet{graal}), a \textit{Passion} and a \textit{Vie de Saint Leger}  (\citet{old_french_corpus}), a \textit{Vie de Saint Thibaut} (\citet{theobaldus}). Neither noise characters nor random keeping of words were applied.

@@

\begin{table}[!ht]
\centering
\begin{tabular}{lllllll}
\hline
 & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & 0.882 & 0.893 & 0.808 & 0.838 & 3658 & 644 \\
CNN P & \textbf{0.957} & \textbf{0.948} & \textbf{0.944} & \textbf{0.945} & \textbf{854} & \textbf{723} \\ \hline
\end{tabular}
\caption{Scores over the unknown dataset. FN = False Negative, FP = False Positive}
\label{tab:scores_unknown}
\end{table}

\subsubsection{Example of outputs}

@@

\subsection{Evaluation on Latin data}

For the following evaluations, the same process was deployed: CNN without Position was evaluated against the baseline on both a test set composed by the same texts that the training text, and an unknown corpora composed by unseen texts.

\subsubsection{Latin Prose and Poetic Corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.978 & 0.961 & 0.974 & 0.968 & 886 & 1893 \\
CNN P & Test & \textbf{0.992} & \textbf{0.987} & \textbf{0.989} & \textbf{0.988} & \textbf{439} & \textbf{584} \\ \hline
Baseline & Unknown & 0.933 & 0.897 & 0.890 & 0.893 & 1587 & 1409 \\
CNN P & Unknown & 0.970 & 0.952 & 0.956 & 0.954 & 600 & 709 \\ \hline
\end{tabular}
\caption{Scores over the Latin classical datasets. FN = False Negative, FP = False Positive}
\label{tab:latin_corpora}
\end{table}

The Latin data is much more noisy than the Old French, as it was less curated than the digital edition provided for Old French. They are part of the Perseus corpus \citet{perseus} and were cut into passages in the context of my thesis. The training, evaluation and test corpora are built upon prose works from Cicero and Suetonius. The unknown corpus is built upon \textit{Epigrammata} from Martial, from book 1 to book 2, as it should be fairly different in word order, vocabulary, etc. Both corpus were generated without noise and word keeping, with a maximum sample size of 150 characters.

\textbf{Statistics:}
\begin{itemize}
\item Number of training examples: 30725
\item Number of evaluation examples: 3558
\item Number of testing examples: 4406
\item Number of classes in testing examples: 105,915 WC; 26,404 WB
\item Number of classes in unknown examples: 35,910 WC; 8,828 WB
\end{itemize}

@@

\subsubsection{Medieval Latin corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.989 & 0.981 & 0.986 & 0.982 & 1036 & 933 \\
CNN P & Test & \textbf{0.997} & \textbf{0.995} & \textbf{0.995} & \textbf{0.995} & \textbf{251} & \textbf{298} \\ \hline
Baseline & Unknown & 0.929 & 0.900 & 0.865 & 0.881 & 14,382 & 27,019 \\
CNN P & Unknown & 0.976 & 0.960 & 0.963 & 0.962 & 6509 & 7444\\ \hline
\end{tabular}
\caption{Scores over the Latin medieval datasets. FN = False Negative, FP = False Positive}
\label{tab:medieval_latin_corpora}
\end{table}

@@

The medieval Latin corpora is based on the project Formulae - Litterae - Chartae's open data (\citet{formulae}) for its training, evaluation and test sets; the unknown corpora is based on three texts from the Monumenta Germanica (\citet{germanica}) that are from early to late medieval period (Andreas Agnellus, Manegaldus, Theodoricus de Niem) and are drawn from the Corpus Corporum Project. Both corpus were generated without noise and word keeping, with a maximum sample size of 150 characters. The data presents some MUFI characters but still look like mostly normalized editions, unlike the Old French data.

@@

\begin{itemize}
\item Number of training examples: 36814
\item Number of evaluation examples: 4098
\item Number of testing examples: 5612
\item Number of classes in testing examples: 137,465 WC; 34,053 WB
\item Number of classes in unknown examples: 472,655 WC; 113,004 WB
\end{itemize}p

@@

\subsubsection{Latin epigraphic corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.956 & 0.935 & 0.943 & 0.939 & 2646 & 3547 \\
CNN P & Test & \textbf{0.987} & \textbf{0.983} & \textbf{0.979} & \textbf{0.981} & \textbf{1149} & \textbf{722} \\ \hline
Baseline & Test Uppercase & 0.956 & 0.935 & 0.942 & 0.938 & 2664 & 3457 \\
CNN P & Test Uppercase & \textbf{0.979} & \textbf{0.972} & \textbf{0.967} & \textbf{0.969} & \textbf{1715} & \textbf{1275} \\ \hline
Baseline & Unknown & 0.879 & 0.834 & 0.817 & 0.825 & 8693 & 11332 \\
CNN P & Unknown & 0.953 & 0.939 & 0.926 & 0.932 & 4689 & 3112 \\ \hline
Baseline & Unknown Uppercase & 0.879 & 0.834 & 0.817 & 0.825 & 8693 & 11332 \\
CNN P & Unknown Uppercase & 0.936 & 0.914 & 0.902 & 0.908 & 6152 & 4464 \\ \hline
\end{tabular}
\caption{Scores over the Latin epigraphic datasets. FN = False Negative, FP = False Positive}
\label{tab:epigraphyc_latin}
\end{table}

@@

The epigraphic Latin corpora is based on the Epigraphic Database Heidelberg open data \citet{formulae} for its training, evaluation and test sets (HD000001-HD010000 and HD010001-HD020000 from \citet{edh}) while the corpus of unknown is drawn from an automatic conversion of the Pompei Inscriptions (\citet{pompei}). Both the baseline and the model were evaluated on uppercase data, as it would normally be the state the text would be found in. Each of the corpora presents a high number of unresolved abbreviations (\textit{ie.} one letter words). Both corpus were generated without noise and word keeping, with a maximum sample size of 150 characters. The data presents some polytonic Greek characters, some sample being only in Greek.

@@

\begin{itemize}
\item Number of training examples: 46,423
\item Number of evaluation examples: 5,802
\item Number of testing examples: 5,804
\item Number of classes in testing examples: 107,963 WC; 31,900 WB
\item Number of classes in unknown examples: 127,268 WC; 38,055 WB
\end{itemize}

@@

While the baseline performed unexpectedly well on the test corpus, the CNN model definitely performed better on a completely unknown corpus. In this context, the proposed model actually shows its ability to carry over unknown corpora in a better way than classical n-gram approaches. In light of the high accuracy of the CNN model, the model should perform the same way independently of the language in Medieval Western Europe,.

@@

Achieving 0.99 accuracy on word segmentation with a corpus as large as 25,000 test samples seems to be the first step for a more thorough data mining of OCRed manuscript. Given the results, studying the importance of normalization and lowering should probably be a further step, as it might be of high influence in smaller corpora.

@@

Boudams has been made possible by two open-source repositories from which I learned and copied bits of implementation of certain modules and without which none of this paper would have been possible: \citet{enrique_manjavacas_2019_2654987} and \citet{bentrevett}. This tool was originally intended for post-processing OCR for the presentation \citet{pinchecampsclerice} at DH2019 in Utrecht.

>>>>

\documentclass{jdmdh}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{tabularx}
\usepackage{titlesec}

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{1.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\newcolumntype{C}{>{\arraybackslash}X} % centered "X" column

@@

Tokenization of spaceless strings is a task that is specifically difficult for computers as compared to "whathumanscando". \textit{Scripta continua} is a western Latin writing phenomenon in which words are separated by spaces. It disappeared around the 8th century (see \citet{zanna1998lecture}), but, nevertheless, spacing remained erratic \footnote{From a modern point of view. What we call here \textit{scripta continua} ranges from traditional \textit{scripta continua} to variable spacing writing.} in later centuries writing as \citet{stutzmann} explains (\textit{cf.} Figure \ref{fig:4lines}). The fluctuation of space width, or simply their presence becomes an issue for OCR. Indeed, in the context of text mining of HTR or OCR output, lemmatization and tokenization of medieval western languages is quite often a pre-processing step for further research to sustain analyses such as authorship attribution, corpus linguistics or simply allow full-text search \footnote{We have found no previous study of \textit{scripta continua} and the likes as a natural language processing issue, only as an HTR/OCR one, such as \cite{wahlberg2014spotting} and \cite{8269990}}.

@@

It must be stressed in this study that the difficulty inherent to segmentation is different for \textit{scripta continua} than the one for languages such as Chinese for which an already impressive amount of work has been done. Indeed, the dimensionality alone of Chinese character set is different from Latin alphabets \footnote{a range of twenty to few hundred characters if we take into account all diacritic combination in Latin scripts, at least few thousands in Chinese, depending on the period \cite{routledge}}, and the important presence of compounds is definitely an issue for segmentation \footnote{According to \cite{tse2017chinese}, \textit{"about 73.6 \% of modern Chinese words are two-character compound words".}}. Chinese word segmentation has lately been driven by deep learning methods: \citet{chen2015long} defines a process based on LSTM model, while \citet{yu2019learning} uses bi-directional GRU and CRF. \footnote{\citet{huang2019realistic} actually gave us the denomination used here: word boundary (WB) and word content (WC).}

@@

For evaluation purposes, and to reduce the amount of input classes, two options for data transcoding were used: a lower-case normalization and a "reduction to the ASCII character set" feature (fr. \ref{fig:normalization}). On this point, a lot of issues were encountered with transliteration of medieval paelographic characters that were part of the original datasets, as they are poorly interpreted by the \texttt{unidecode} python package. Indeed, \texttt{unidecode} will simply remove characters it does not understand. A derivative package named \texttt{mufidecode} was built for this reason(\citet{thibault_clerice_2019_3237731}): it takes precedent over \texttt{unidecode} equivalency tables when the data is known of the Medieval Unicode Font Initiative (MUFI, \citet{mufi}).

@@

Aside from normalization of the input and output, three different model structures were tested. Every model is composed of one encoder, as described below, and one Linear Classifier which classifies into 5 classes : Start of Sentence (= SOS), End of Sentence (= EOS), Padding (= PAD), Masked Token (= Word Content), Space (= Word Boundary) \footnote{For final scores, SOS, EOS and PAD were ignored.}.

The encoders are the following (configurations in parentheses):

@@

% We evaluated the tool on different languages, namely Old French and Latin from different eras or writing traditions. Old French is the only language on which all model configurations were tested, Latin was tested only on the best performing configuration against the baseline.

\subsubsection{Evaluation on Old French Data}

\paragraph{Main Dataset}

@@

\begin{itemize}
    \item 193,734 training examples (group of words);
    \item 23,581 validation examples;
    \item 25,512 test examples
    \item Number of classes in testing examples: 482,776 WC; 169,094 WB
\end{itemize}

Examples were generated automatically. They are between 2 and 8 words-length. In order to recreate the condition of OCR noise, full stop characters were added randomly (20\% chance) between words. In order to augment the dataset, words are randomly (10\% chance) passed over the next example\footnote{This data augmentation was limited to one word per sample}. If a minimum size of 7 characters was not met in the input sample, another word would be added to the chain, independently of the maximum number of words. The example however should not go beyond 100 characters. The results corpora should be varied in sizes as shown by Figure \ref{fig:word_sizes}. The corpora contains 193 different characters when not normalized, in which some MUFI characters appears few hundred times (\textit{cf.} Table \ref{tab:mufi_examples}).

@@

\paragraph{Results}

@@

\paragraph{Out-of-domain (OUD) texts}

While all models using CNN show improvement over the baseline, the models definitely do not significantly outperform (\textless 0.02 FScore). There is a reason for this: the baseline already performs nearly perfectly on the test corpus. The dictionary attack using n-grams did actually perform well. Therefore, an additional evaluation method was constructed. The baseline and the best achieving deep-learning model (CNN P) were evaluated on a secondary test corpus composed of texts of a different domain. This new corpus is composed of 4 texts and counts 742 examples : the diplomatic edition of the \textit{Graal} (\citet{graal}), a \textit{Passion} and a \textit{Vie de Saint Leger}  (\citet{old_french_corpus}), a \textit{Vie de Saint Thibaut} (\citet{theobaldus}). Neither noise characters nor random keeping of words were applied. The resulting corpus contains 26,393 WC and 10,193 WB.

@@

\begin{table}[!ht]
\centering
\begin{tabular}{lllllll}
\hline
 & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & 0.882 & 0.893 & 0.808 & 0.838 & 3658 & 644 \\
CNN P & \textbf{0.957} & \textbf{0.948} & \textbf{0.944} & \textbf{0.945} & \textbf{854} & \textbf{723} \\ \hline
\end{tabular}
\caption{Scores over the out-of-domain dataset. FN = False Negative, FP = False Positive}
\label{tab:scores_unknown}
\end{table}

\paragraph{Example of Outputs}

@@

\subsubsection{Evaluation on Latin data}

For the following evaluations, the same process was deployed: CNN without Position was evaluated against the baseline on both a test set composed by the same texts that the training text, and an out-of-domain corpus composed by unseen texts. Evaluation has been done on three different kind of Latins (edited, classical Latin (1); medieval Latin of charters (2); epigraphic Latin (3)) as they show different level of difficulties: they always present rich morphology, but medieval Latin displays spelling variations while epigraphic Latin displays both spelling variation and a high presence of abbreviations.

\paragraph{Latin Prose and Poetic Corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.978 & 0.961 & 0.974 & 0.968 & 886 & 1893 \\
CNN P & Test & \textbf{0.992} & \textbf{0.987} & \textbf{0.989} & \textbf{0.988} & \textbf{439} & \textbf{584} \\ \hline
Baseline & OUD & 0.933 & 0.897 & 0.890 & 0.893 & 1587 & 1409 \\
CNN P & OUD & 0.970 & 0.952 & 0.956 & 0.954 & 600 & 709 \\ \hline
\end{tabular}
\caption{Scores over the Latin classical datasets. FN = False Negative, FP = False Positive}
\label{tab:latin_corpora}
\end{table}

The Latin data is much noisier than the Old French, as it was less curated than the digital edition provided for Old French. They are part of the Perseus corpus \citet{perseus} and were cut into passages in the context of my thesis. The training, evaluation and test corpora are built upon prose works from Cicero and Suetonius. The out-of-domain corpus is built upon \textit{Epigrammata} from Martial, from book 1 to book 2, as it should be fairly different in word order, vocabulary, etc. Both corpora were generated without noise and word keeping, with a maximum sample size of 150 characters.

\textbf{Statistics:}
\begin{itemize}
\item Number of training examples: 30725
\item Number of evaluation examples: 3558
\item Number of testing examples: 4406
\item Number of classes in testing examples: 105,915 WC; 26,404 WB
\item Number of classes in OUD examples: 35,910 WC; 8,828 WB
\end{itemize}

@@

\paragraph{Medieval Latin corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.989 & 0.981 & 0.986 & 0.982 & 1036 & 933 \\
CNN P & Test & \textbf{0.997} & \textbf{0.995} & \textbf{0.995} & \textbf{0.995} & \textbf{251} & \textbf{298} \\ \hline
Baseline & OUD & 0.929 & 0.900 & 0.865 & 0.881 & 14,382 & 27,019 \\
CNN P & OUD & 0.976 & 0.960 & 0.963 & 0.962 & 6509 & 7444\\ \hline
\end{tabular}
\caption{Scores over the Latin medieval datasets. FN = False Negative, FP = False Positive}
\label{tab:medieval_latin_corpora}
\end{table}

@@

The medieval Latin corpus is based on the project Formulae - Litterae - Chartae's open data (\citet{formulae}) for its training, evaluation and test sets; the out-of-domain corpora is based on three texts from the Monumenta Germanica (\citet{germanica}) that are from early to late medieval period (Andreas Agnellus, Manegaldus, Theodoricus de Niem) and are drawn from the Corpus Corporum Project. Both corpora were generated without noise and word keeping, with a maximum sample size of 150 characters. The data presents some MUFI characters but still look like mostly normalized editions, unlike the Old French data.

@@

\begin{itemize}
\item Number of training examples: 36814
\item Number of evaluation examples: 4098
\item Number of testing examples: 5612
\item Number of classes in testing examples: 137,465 WC; 34,053 WB
\item Number of classes in OUD examples: 472,655 WC; 113,004 WB
\end{itemize}

@@

\paragraph{Latin epigraphic corpora}

\begin{table}[H]
\centering
\begin{tabular}{llllllll}
\hline
 & Corpus & Accuracy & Precision & Recall & FScore & WB FN & WB FP \\ \hline
Baseline & Test & 0.956 & 0.935 & 0.943 & 0.939 & 2646 & 3547 \\
CNN P & Test & \textbf{0.987} & \textbf{0.983} & \textbf{0.979} & \textbf{0.981} & \textbf{1149} & \textbf{722} \\ \hline
Baseline & Test Uppercase & 0.956 & 0.935 & 0.942 & 0.938 & 2664 & 3457 \\
CNN P & Test Uppercase & \textbf{0.979} & \textbf{0.972} & \textbf{0.967} & \textbf{0.969} & \textbf{1715} & \textbf{1275} \\ \hline
Baseline & OUD & 0.879 & 0.834 & 0.817 & 0.825 & 8693 & 11332 \\
CNN P & OUD & 0.953 & 0.939 & 0.926 & 0.932 & 4689 & 3112 \\ \hline
Baseline & OUD Uppercase & 0.879 & 0.834 & 0.817 & 0.825 & 8693 & 11332 \\
CNN P & OUD Uppercase & 0.936 & 0.914 & 0.902 & 0.908 & 6152 & 4464 \\ \hline
\end{tabular}
\caption{Scores over the Latin epigraphic datasets. FN = False Negative, FP = False Positive}
\label{tab:epigraphyc_latin}
\end{table}

@@

The Latin epigraphic corpus is based on the Epigraphic Database Heidelberg open data \citet{formulae} for its training, evaluation and test sets (HD000001-HD010000 and HD010001-HD020000 from \citet{edh}) while the out-of-domain corpus is drawn from an automatic conversion of the Pompei Inscriptions (\citet{pompei}). Both the baseline and the model were evaluated on uppercase data, as it would normally be the state the text would be found in. Each of the corpora presents a high number of unresolved abbreviations (\textit{ie.} one letter words). Both corpora were generated without noise and word keeping, with a maximum sample size of 150 characters. The data presents some polytonic Greek characters, some sample being only in Greek.

@@

\begin{itemize}
\item Number of training examples: 46,423
\item Number of evaluation examples: 5,802
\item Number of testing examples: 5,804
\item Number of classes in testing examples: 107,963 WC; 31,900 WB
\item Number of classes in OUD examples: 127,268 WC; 38,055 WB
\end{itemize}

@@

While the baseline performed unexpectedly well on the test corpus, the CNN model definitely performed better on a out-of-domain corpus. In this context, the proposed model actually shows its ability to carry over unknown corpora in a better way than classical n-gram approaches. In light of the high accuracy of the CNN model, the model should perform the same way independently of the language in Medieval Western Europe.

@@

Achieving 0.99 accuracy on word segmentation with a corpus as large as 25,000 test samples seems to be the first step for a more thorough data mining of OCRed manuscripts. Given the results, studying the importance of normalization and lowering should probably be a further step, as it might be of high influence in smaller corpora.

@@

Boudams has been made possible by two open-source repositories from which I learned and copied bits of the implementation of certain modules and without which none of this paper would have been possible: \citet{enrique_manjavacas_2019_2654987} and \citet{bentrevett}. This tool was originally intended for post-processing OCR for the presentation \citet{pinchecampsclerice} at DH2019 in Utrecht.
